### 2019-02-22 sections/relatedwork.tex
Added related work common intro
Added mtasks cite to related work

\fixme{Intro related work}

@@

The \MTASKS framework is an implementation of \TOP geared towards \IOT devices.
As \TOPHAT its basic combinators are a subset of \ITASKS.
They are similar to those of \TOPHAT.
However, on \IOT devices it is useful to continue running tasks endlessly,
which is done in \MTASKS using a \CL{forever} combinator.
This is currently not possible in \TOPHAT.

>>>>

The work presented in this paper lies on the boundary of many areas of study.
People have looked at the problem of how to model and coordinate collaboration from many different perspectives.
The following subsections give an overview of related work from the many different areas.

@@

The \MTASKS framework \cite{koopman2018task} is an implementation of \TOP geared towards \IOT devices.
As \TOPHAT its basic combinators are a subset of \ITASKS.
They are similar to those of \TOPHAT.
However, on \IOT devices it is useful to continue running tasks endlessly,
which is done in \MTASKS using a \CL{forever} combinator.
This is currently not possible in \TOPHAT.
